Gammapy: A Python package for gamma-ray astronomy

### 2023-05-25 src/ms-review.tex
Fix build after implementing comments

Figure~\ref{fig:data_flow} shows an overview of the different sub-packages and
their relation to each other. The \code{gammapy.data} and \code{gammapy.irf}
sub-packages define data objects to represent DL3 data, such as
event lists and IRFs as well as functionality
to read the DL3 data from disk into memory. The \code{gammapy.makers} sub-package
contains the functionality to reduce the DL3 data to binned maps.
Binned maps and datasets, which represent a collection of binned
maps, are defined in the \code{gammapy.maps} and \code{gammapy.datasets}
sub-packages, respectively. Parametric models, which are defined in
\code{gammapy.modeling}, are used to jointly model a combination
of datasets, for example, to compute a spectrum using data from several facilities. Estimator classes,
which are contained in \code{gammapy.estimators}, are used to
compute higher level science products such as flux and significance maps,
light curves or flux points. Finally there is a \code{gammapy.analysis}
sub-package which provides a high-level interface for executing analyses
defined from configuration files. In the following sections, we will
introduce all sub-packages and their functionalities in more detail.

@@

Some example IRFs read from public data files and plotted with \gammapy are shown 
in Figure~\ref{fig:irfs}.

@@

@@

@@

@@

@@

The model gallery\footnote[number]{\url{https://docs.gammapy.org/1.0/user-guide/model-gallery/index.html}}
 provides a visual overview of the available models in
\gammapy. Most of the analytic models commonly used in \gammaray astronomy are
built-in. We also offer a wrapper to radiative models implemented in the Naima
package~\citep{naima}. The modeling framework can be easily extended with
user-defined models. For example, the radiative models of jetted Active Galactic Nuclei (AGN)
implemented in \agnpy~\citep{agnpy2022}, can be wrapped into 
\gammapy~\citep[see Section 3.5 of ][]{2022A&A...660A..18N}. We provide 
more examples of user-defined models, such as a parametric model for energy dependent morphology,
in the online documentation\footnote[number]{\url{https://docs.gammapy.org/1.0/tutorials/api/models.html#implementing-a-custom-model}}.

@@

@@

More examples for modelling the broadband emission of \gammaray sources, which 
partly involve \gammpy are available in the online documentation of the
Agnpy, Naima, Jetset and Gamera packages\footnote{\url{https://agnpy.readthedocs.io/en/latest/tutorials/ssc_gammapy_fit.html}},
\footnote{\url{https://naima.readthedocs.io/en/stable/tutorial.html}}, 
\footnote{\url{https://jetset.readthedocs.io/en/stable/user_guide/documentation_notebooks/gammapy_plugin/gammapy_plugin.html}},
\footnote{\url{http://libgamera.github.io/GAMERA/docs/fitting_data.html}}.

@@

\begin{itemize}
	\item[a] The \iacts data reduction step is done in the same way described in the 
	previous sections but scaled up to few thousands of observations. This step can be
	trivially parallelised by deploying the \gammapy package on a cluster.
	\item[b] The object detection step typically consists in finding local maxima
	in the significance or TS maps, computed by the \code{ExcessMapEstimator} or
	\code{TSMapEstimator} respectively. For this \gammapy provides a simple \code{find_peaks}
	method. For more advanced methods users can rely on 3rd party packages such as
	\textit{Scikit-image}~\citep{scikit-image}. This packages provide e.g. general
	blob detection algorithms and image segmentation methods such as hysteresis thresholding
	or the watershed transform. 	
	\item[c] During the modelling step each object is alternatively fitted with different
	models in order to determine their optimal parameters, and the best-candidate model. The
	subpackage \code{gammapy.modeling.models} offers a large variety of choices for spatial
	and spectral models as well as the possibility to add custom models. For the model selection
	\gammapy provides statisticl helper methods to perform likelihood ratio tests.
	But users can also rely on 3rd party packages such as \textit{Scikit-learn}~\citep{scikit-learn}
	to compute quantities such as the Akaike information criterion (AIC) or the Bayesian
	information criterion (BIC), which also allow for model selection.
	\item[d] For the association and classification step, which is tightly connected to
	population studies, we can easily compare the fitted models to the set of
	existing \gammaray catalogs available in \code{gammapy.catalog}. Further
	multi-wavelength cross-matches are usually required to characterize the
	sources. This can easily be achieved by relying on coordinate
	handling from Astropy in combination with affiliated packages such as
	\textit{Astroquery}~\citep{astroquery}. For more advanced source classification
	methods users can again rely e.g. \textit{Scikit-learn} to perform supervised
	or unsupervised clustering.
\end{itemize}

>>>>

Figure~\ref{fig:data_flow} shows an overview of the different sub-packages and
their relation to each other. The \code{gammapy.data} and \code{gammapy.irf}
sub-packages define data objects to represent DL3 data, such as
event lists and IRFs as well as functionality
to read the DL3 data from disk into memory. The \code{gammapy.makers} sub-package
contains the functionality to reduce the DL3 data to binned maps.
Binned maps and datasets, which represent a collection of binned
maps, are defined in the \code{gammapy.maps} and \code{gammapy.datasets}
sub-packages, respectively. Parametric models, which are defined in
\code{gammapy.modeling}, are used to jointly model a combination
of datasets, for example, to compute a spectrum using data from several facilities. Estimator classes,
which are contained in \code{gammapy.estimators}, are used to
compute higher level science products such as flux and significance maps,
light curves or flux points. Finally there is a \code{gammapy.analysis}
sub-package which provides a high-level interface for executing analyses
defined from configuration files. In the following sections, we will
introduce all sub-packages and their functionalities in more detail.
In the online documentation we also provide an overview of all
the \gammapy sub-packages\footnote{\url{https://docs.gammapy.org/1.0/user-guide/package.html}}.q

@@

Some example IRFs read from public data files and plotted with \gammapy are shown 
in Figure~\ref{fig:irfs}. More information on \code{gammapy.irf} can be found 
in the online documentation\footnote{\url{https://docs.gammapy.org/1.0/user-guide/irf/index.html\#irf}}.

@@

More information on the \code{gammapy.maps} sub-module can be found 
in the online documentation\footnote{\url{https://docs.gammapy.org/1.0/user-guide/maps/index.html\#maps}}.

@@

We also refer to our online documentation for more details on \code{gammapy.datasets}
\footnote{\url{https://docs.gammapy.org/1.0/user-guide/datasets/index.html\#datasets}}.

@@

More detailed information on the \code{gammapy.makers} sub-package is available online\footnote{\url{https://docs.gammapy.org/1.0/user-guide/makers/index.html\#makers}}.

@@

Our online documentation provides more information on \code{gammapy.stats}
\footnote{\url{https://docs.gammapy.org/1.0/user-guide/stats/index.html\#stats}}.

@@

The model gallery\footnote{\url{https://docs.gammapy.org/1.0/user-guide/model-gallery/index.html}}
 provides a visual overview of the available models in
\gammapy. Most of the analytic models commonly used in \gammaray astronomy are
built-in. We also offer a wrapper to radiative models implemented in the Naima
package~\citep{naima}. The modeling framework can be easily extended with
user-defined models. For example, the radiative models of jetted Active Galactic Nuclei (AGN)
implemented in \agnpy~\citep{agnpy2022}, can be wrapped into 
\gammapy~\citep[see Section 3.5 of ][]{2022A&A...660A..18N}. We provide 
more examples of user-defined models, such as a parametric model for energy dependent morphology,
in the online documentation\footnote{\url{https://docs.gammapy.org/1.0/tutorials/api/models.html\#implementing-a-custom-model}}.

@@

More details on the \code{gammapy.estimators} sub-module are available online \footnote{\url{https://docs.gammapy.org/1.0/user-guide/estimators.html\#estimators}}.

@@

More examples for modelling the broadband emission of \gammaray sources, which 
partly involve \gammapy are available in the online documentation of the
Agnpy, Naima, Jetset and Gamera packages\footnote{\url{https://agnpy.readthedocs.io/en/latest/tutorials/ssc\_gammapy\_fit.html}},
\footnote{\url{https://naima.readthedocs.io/en/stable/tutorial.html}}, 
\footnote{\url{https://jetset.readthedocs.io/en/stable/user\_guide/documentation\_notebooks/gammapy\_plugin/gammapy\_plugin.html}},
\footnote{\url{http://libgamera.github.io/GAMERA/docs/fitting\_data.html}}.

@@

\begin{itemize}
	\item[a] The \iacts data reduction step is done in the same way described in the 
	previous sections but scaled up to few thousands of observations. This step can be
	trivially parallelised by deploying the \gammapy package on a cluster.
	\item[b] The object detection step typically consists in finding local maxima
	in the significance or TS maps, computed by the \code{ExcessMapEstimator} or
	\code{TSMapEstimator} respectively. For this \gammapy provides a simple \code{find\_peaks}
	method. For more advanced methods users can rely on 3rd party packages such as
	\textit{Scikit-image}~\citep{scikit-image}. This packages provide e.g. general
	blob detection algorithms and image segmentation methods such as hysteresis thresholding
	or the watershed transform. 	
	\item[c] During the modelling step each object is alternatively fitted with different
	models in order to determine their optimal parameters, and the best-candidate model. The
	subpackage \code{gammapy.modeling.models} offers a large variety of choices for spatial
	and spectral models as well as the possibility to add custom models. For the model selection
	\gammapy provides statisticl helper methods to perform likelihood ratio tests.
	But users can also rely on 3rd party packages such as \textit{Scikit-learn}~\citep{scikit-learn}
	to compute quantities such as the Akaike information criterion (AIC) or the Bayesian
	information criterion (BIC), which also allow for model selection.
	\item[d] For the association and classification step, which is tightly connected to
	population studies, we can easily compare the fitted models to the set of
	existing \gammaray catalogs available in \code{gammapy.catalog}. Further
	multi-wavelength cross-matches are usually required to characterize the
	sources. This can easily be achieved by relying on coordinate
	handling from Astropy in combination with affiliated packages such as
	\textit{Astroquery}~\citep{astroquery}. For more advanced source classification
	methods users can again rely e.g. \textit{Scikit-learn} to perform supervised
	or unsupervised clustering.
\end{itemize}
